---
title: "Lab 1 - Intro to R and RStudio"
author: "Team name"
date: "Date of lab session"
output:
  pdf_document: default
  html_document:
    fig_height: 4
    highlight: pygments
    theme: spacelab
---

```{r setup, include=FALSE}
# DO NOT ALTER CODE IN THIS CHUNK
knitr::opts_chunk$set(echo = TRUE)
```

* * *

## Lab report

#### Load data: (Hint, the `source` command from the lab)
```{r}
source("http://www.openintro.org/stat/data/arbuthnot.R")

```

#### Exercise 1: 
  I would add this block of code to plot the graph:
```{r ex1}
plot(x = arbuthnot$year, y = arbuthnot$girls)
?plot
```

#### Exercise 2: 
  This adds all the boys and girls together for every column in the data.
```{r ex2}
arbuthnot$boys + arbuthnot$girls


```


#### Exercise 3: 


```{r ex3}
arbuthnot$boys > arbuthnot$girls

```




* * *

### On your own:

#### 1:


The years included are from the span of 1940 to 2002. The dimensions are 63x3. The names are year, boys, girls.
```{r oyo1}
source("http://www.openintro.org/stat/data/present.R")
dim(present)
names(present)

```



#### 2:
They are very far from each other


```{r oyo2}
plot(x=present$boys,y=present$girls)
```


#### 3:



```{r oyo3}

```



#### 4:

```{r oyo4}
present$boys + present$girls
plot(x = present$year, y = present$boy+present$girls)
temp = 0
pop = 0
for (i in 1:63)
{;
  if(present$boys[i]+present$girls[i] > pop){;
    pop = present$boys[i]+present$girls[i]
    temp = present$year[i];
  };
};
temp
pop

```


* * *

## Teamwork report

<!--
For each team member, write their name, whether they attended the lab session, 
whether they were the author for this week, and their contribution to the lab 
report (as a percentage). The percentages should add up to 100.
-->

| Team member             | Attendance | Author   | Contribution % |
|:------------------------|:----------:|:--------:|---------------:|
| Name of member 1        | Yes / No   | Yes / No | 25%            |
| Name of member 2        | Yes / No   | Yes / No | 25%            |
| Name of member 3        | Yes / No   | Yes / No | 25%            |
| Name of member 4        | Yes / No   | Yes / No | 25%            |
| Total                   |            |          | 100%           |